This document provides the requirements and design details of the
PROJECT.  The following table (Table \ref{Table::UpdateHistory}) should be
updated by authors whenever major changes are made to the architecture
design or new components are added. Add updates to the top of the table.  
Most recent changes to the document should be seen first and the oldest 
last.

\begin{longtable}{|l||p{13.5cm}|}
%\centering
\caption{Document Update History \label{Table::UpdateHistory}}\\
\hline
\textbf{Date} & \textbf{Updates} \\
\hline 
\endhead

10/16/2025 & RD, IF, JJ
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
    \item Added \hyperref[Chapter::Overleaf and Github Integration]{Overleaf and GitHub Integration} chapter for Homework 6, documenting the connection between Overleaf and GitHub.
    \item Updated \hyperref[Chapter::Hosts]{Hosts} table to include the domain and address of the local LaTeX instance.
\end{itemize}
\\ \hline

10/08/2025 & 
{JJ:}
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
  \item Configured and deployed the Bugzilla container on the DigitalOcean droplet.
  \item Added \hyperref[Chapter::Bugzilla]{Bugzilla} chapter documenting setup, troubleshooting, and verification.
\end{itemize}

{IF:}
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
  \item Deployed and verified the Overleaf Toolkit container on DigitalOcean.
  \item Added \hyperref[Chapter::Overleaf]{Overleaf} chapter detailing configuration, Docker installation, and web access confirmation.
\end{itemize}

{RD:}
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
  \item Updated \hyperref[Chapter::Hosts]{Hosts} table for DigitalOcean.
  \item Updated \hyperref[Chapter::Passwords]{Passwords} table for DigitalOcean.

\end{itemize}
\\ \hline

10/08/2025 & RD, IF, JJ
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
    \item Updated \hyperref[Chapter::Hosts]{Hosts} table for Digital Ocean
    \item Updated \hyperref[Chapter::Passwords]{Passwords} table for Digital Ocean
    \item Added \hyperref[Chapter::Bugzilla]{Bugzilla} chapter displaying Bugzilla docker container configurations for Bugzilla and Overleaf Dockers on Digital Ocean.
    \item Added \hyperref[Chapter!Overleaf]{Overleaf} chapter displaying Overleaf Docker container configurations for Bugzilla and Overleaf Dockers on Digital Ocean assignment.

    \end{itemize}
\\ \hline

10/01/2025 & RD, IF, JJ
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
    \item Added \hyperref[Chapter::AWSDeployment]{AWS deployment} chapter for Docker on AWS homework and added \hyperref[Chapter::LaTeXDocker]{LaTeX Docker}.
\end{itemize}
\\ \hline

09/24/2025 & RD, IF, JJ
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
    \item Added \hyperref[chap:pproposal]{Project Proposal chapter} for our project Figma2AWS
\end{itemize}
\\ \hline

09/14/2025 & RD, IF, JJ
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
    \item Provided solutions for the \hyperref[chap:linux]{Linux Problem Set in the Linux Commands assignment}.
\end{itemize}
\\ \hline

09/03/2025 & RD, IF, JJ:
\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=12pt]
\item Created Kanban board on GitHub 
figures, and other labels.
\end{itemize} 
\\ \hline





\end{longtable}


