\chapter{Hosts \\
\small{\textit{-- Ivan Farfan, Johan Jaramillo, Ryan Davis}}}
\index{Hosts} 
\index{Chapter!Hosts}
\label{Chapter::Hosts}

This chapter lists the primary hosts used for the project deployment.  
Each host represents a service or container deployed within the shared DigitalOcean environment.  
IP addresses and configurations are specific to the development setup for Fall 2025.


\begin{longtable}{|p{4cm}|p{4cm}|p{3cm}|p{6cm}|}
\caption{Project Hosts and Roles} \label{tab:hosts} \\
\hline
\textbf{Hostname / Service} & \textbf{IP Address} & \textbf{Operating System} & \textbf{Role / Purpose} \\
\hline
\endfirsthead

\multicolumn{4}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline
\textbf{Hostname / Service} & \textbf{IP Address} & \textbf{Operating System} & \textbf{Role / Purpose} \\
\hline
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot

\hline
\endlastfoot

Overleaf Container & 167.71.181.60 & Ubuntu 25.04 & Overleaf LaTeX Toolkit deployed via Docker; provides collaborative document editing capabilities. \\
\hline
Bugzilla Container & 167.71.179.151 & Ubuntu 25.04 & Bugzilla issue tracking system deployed in a Docker container for project management and defect tracking. \\
\hline
DigitalOcean Droplet & N/A & Ubuntu 25.04 & Cloud infrastructure host running both the Overleaf and Bugzilla containers within the same droplet environment. \\
\hline
Local Overleaf & ssw590f25.me & Nginx and Ubuntu 25.04 & Public domain that runs our local overleaf version. \\
\hline
Load Balancer and Virtual Host & 143.198.5.82 & Nginx and Ubuntu & Deploys our load balanced website, and virtual hosted web1 and web2 domains
\hline
Figma2Deployment & 159.203.129.168 & Ubuntu 25.04 & Deploys our Figma2Deployment plugin, deploying websites created on Figma to a port in the droplet.
\hline

\end{longtable}

