\chapter{Passwords \\
\small{\textit{-- Ivan Farfan, Johan Jaramillo, Ryan Davis}}}
\index{Passwords} 
\index{Chapter!Passwords}
\label{Chapter::Passwords}
 
\begin{longtable}{|p{3cm}|p{13cm}|}
\hline
\textbf{Category} & \textbf{Password Rule} \\
\hline
\endfirsthead

\hline
\textbf{Category} & \textbf{Password Rule} \\
\hline
\endhead

% ---------- Server Rules ----------
Server Rules & 
\begin{itemize}
    \item We use a prefix for the site (which city the server is in), then a descriptive shorthand for what the server does. 
    \item Example: \texttt{XXFS01} would be a file server in location \texttt{XX}. 
    \item If there were a second file server in the same location, it would be named \texttt{XXFS02}.
\end{itemize} \\
\hline

% ---------- User Rules ----------
User Rules & 
\begin{itemize}
    \item Passwords must be changed every 60 days.
    \item Users cannot reuse the last 4 passwords.  
    \item Accounts will be locked after 3 failed login attempts.
\end{itemize} \\
\hline

% ---------- General Rules ----------
General Rules & 
\begin{itemize}
    \item Passwords must have at least 10 characters.
    \item Passwords must include at least one uppercase letter.
    \item Passwords must include at least one lowercase letter.
    \item Passwords must include at least one special character (e.g., !, @, \#, \$).
\end{itemize} \\
\hline

% ---------- Custom Rule ----------
Custom Rule & 
\begin{itemize}
    \item Include the abbreviation of the operating system you use. 
    \item Finish with a memorable number, such as the year of graduation or the current semester.
\end{itemize} \\
\hline



% ---------- Digital Ocean ----------
Digital Ocean & 
\begin{itemize}
    \item Follows the standardized password pattern:
    \begin{center}
        \texttt{<coursetag><coursenumber><termLetter>@<serviceInitials>}
    \end{center}
    \item The initials \texttt{do} represent DigitalOcean.
    \item This ensures service-specific uniqueness across all deployed systems.
\end{itemize} \\
\hline

\end{longtable}



\section*{Hints}
\begin{itemize}
    \item User passwords often mix in course codes, semesters, or graduation years. 
    \item General passwords follow the 10+ character, uppercase, lowercase, and special character requirements. 
    \item Custom group passwords contain a Mac/OS reference combined with a number tied to student life.
\end{itemize}